Are Solar Panels Commodities? A Bayesian Hierarchical Approach to Detecting Quality Differences and Asymmetric Information.

### 2019-07-02 ejor_submission/R&R2/rr2_mauritzenJune19.tex
Final push after acceptance

@@

@@

More formally, a commodity is generally defined by a certain degree of fungibility. That is, the good from a certain producer will be largely interchangeable with the good of another producer. Already in 1873 the German economist A.E.F. Schäffle distinguished between a popular understanding of a commodity as a material input in manufacturing, to the scientific understanding as "exchangeable material goods" \citep{menger_principles_2007}. Despite the simplicity of this definition, \citet{gordon_what_1999} show the difficulty in practice of determining whether a product is in fact a commodity. The root problem is that a good can be differentiated in a host of ways, some of which are difficult to observe at the time of transaction.

@@

An important differentiating characteristic between solar panels is the quality of these solar panels. This can be measured as both the failure rate of these panels as well as the degree of degradation of the panels over time. If there were significant differences in quality between manufacturers, then this has implications for the structure and development of the solar panel market. Manufacturers with superior quality could differentiate themselves and extract a premium in the market. A reputation for quality among established manufacturers could also act as a barrier to entry, thereby reducing long-term pricing pressure.

From the perspective of a purchasing manager responsible for procuring solar panels, whether panels can be considered a commodity is of great importance. If panels are known to be commodities with standardised quality and similar pricing, then the decision for purchasing manager is substantially simplified. They need only to decide on the observable form factor, for example dimension and capacity. In addition, purchasing managers responsible for large projects with long lead times could make use of forward markets to hedge price movements. On the other hand, if solar panels are known to vary significantly by quality, then the decision becomes substantially more complex and costly. Purchasing managers would need to weigh the price of panels against expected quality. They may also need to make use of specialised engineering firms that test and certify panel quality. Since the purchasing decision is likely to be linked to a specific manufacturer, the purchasing manager is subject to risks such as bankruptcy or other supply disruption associated with that firm.

@@

More so, solar panel systems are expected to last at least 20 years, thus for all practical purposes, their purchase can be considered a one-shot investment. This eliminates repeat buying as a mechanism for ensuring quality. In the literature, warranties are often suggested as a strong signal of quality. However, warranties may be a relatively weak assurance of quality in the market for solar panels as both contractors and manufacturers are relatively new, tend to be heavily indebted and some have recently shown a tendency to go bankrupt.

@@

Early theoretical work of particular relevance to this paper includes \citet{chan_prices_1982}, whom model the situation where information on quality is costly rather than directly unavailable and where quality is endogenous to the seller--in other words the seller can choose the level of quality of its product. Under these assumptions, the authors predict several equilibrium--essentially markets for both high- and low-quality products depending on the extent to which the buyer is informed.

>>>>

%%Version sent in for second revision

@@

Solar power has been the fastest growing source of energy generation in recent decades\footnote{\url{https://www.iea.org/topics/renewables/solar/}}, and a large and growing literature within operations research addresses the challenges associated with this technology. One branch of the literature considers the operation of electricity markets and transmission planning with large shares of solar and other intermittent energy (see for example \citet{gianfreda_stochastic_2018}, \citet{pritchard_single_settlement_2010}, or \citet{morales_electricity_2014}). This article, however, contributes to the branch of the literature that concerns investment decisions, procurement and supply chains for solar power. A popular approach has been designing mulitcriteria decision models (MCDM) for solar investment and planning decisions. Here, multicriteria takes on  a range of meanings. For example it can mean modelling dueling objectives between governments and developers \citep{garcia-bernabeu_photovoltaic_2016}. Alternatively, it can refer to the decision of a planner who must balance financial considerations with environmental and social factors \citep{georgopoulou_multicriteria_1997, henao_multicriteria_2012,linares_multiple_2000}, or analysing how multiple sources of risk, such as prices and weather, inform the design decisions of a photovoltaic plant \citep{merzifonluoglu_photovoltaic_2018}. Finally, and most closely related to the subject of this article, a multicriteria decision model can refer to the decision of choosing a certain type of solar panel. \citet{socorro_garcia-cascales_evaluation_2012}, for example, analyses the decision of choosing panel characteristics such as monocrystalline vs. polycrystalline or alternatively, various thin-film type panels. The criteria used for choosing a certain type of cell include manufacturing cost, efficiency, and emissions of greenhouse gases during manufacturing. Notably, however, an analysis of procuring solar panels of uncertain quality and reliability does not exist in the literature, to the best of my knowledge.

@@

More formally, a commodity is generally defined by a certain degree of fungibility. That is, the good from a certain producer will be largely interchangeable with the good of another producer. Already in 1873 the German economist A.E.F. Schäffle distinguished between a popular understanding of a commodity as a material input in manufacturing, to the scientific understanding as "exchangeable material goods" \citep{menger_principles_2007}. In a more recent, but similar definition, \citet{reimann_toward_2010} defines the concept of commoditization as ``occuring when competitors in comparatively stable industries offer increasingly homogenous products.''  Despite the simplicity of these definitions, \citet{gordon_what_1999} show the difficulty in practice of determining whether a product is in fact a commodity. The root problem is that a good can be differentiated in a host of ways, some of which are difficult to observe at the time of transaction.

An important differentiating characteristic between solar panels is the quality of these solar panels. This can be measured as both the failure rate of these panels as well as the degree of degradation of the panels over time. This definition is in line with the general understanding of quality within operations research and economics as "performance quality" \citep{karmarkar_quality_1997}. If there were significant differences in quality between manufacturers, then this has implications for the structure and development of the solar panel market. Manufacturers with superior quality could differentiate themselves and extract a premium in the market . A reputation for quality among established manufacturers could also act as a barrier to entry, thereby reducing long-term pricing pressure \citep{karaer_quality_2015}.

@@

From the perspective of a purchasing or supply chain manager responsible for procuring solar panels, whether panels can be considered a commodity is of great importance. If panels are known to be commodities with standardised quality and similar pricing, then the decision for purchasing manager is substantially simplified. They need only to decide on the observable form factor, for example dimension and capacity. In addition, purchasing managers responsible for large projects with long lead times could make use of forward markets to hedge price movements. On the other hand, if solar panels are known to vary significantly by quality, then the decision becomes substantially more complex and costly. Purchasing managers would need to weigh the price of panels against expected quality. They may also need to make use of specialised engineering firms that test and certify panel quality. Since the purchasing decision is likely to be linked to a specific manufacturer, the purchasing manager is subject to risks such as bankruptcy or other supply disruption associated with that firm.

@@

More so, solar panel systems are expected to last at least 20 years, thus for all practical purposes, their purchase can be considered a one-shot investment. This eliminates repeat buying as a mechanism for ensuring quality. In the literature, warranties are often suggested as a strong signal of quality \citet{murthy_product_2004, murthy_product_2006}. However, warranties may be a relatively weak assurance of quality in the market for solar panels as both contractors and manufacturers are relatively new, tend to be heavily indebted and some have recently shown a tendency to go bankrupt.

@@

Issues of asymmetric information of quality in supply chains and purchasing manager decisions have become prominent in the operations research literature. \citet{quigley_supplier_2018}, noting that validating the quality of suppliers is expensive, develop a model to optimally choose an investment level for ensuring quality of supplies. \citet{nagurney_spatial_2014} model a situation with information asymmetry of quality with multiple supply and demand markets, where spatial distance is correlated to information asymmetry. This model was motivated by an increasingly globalised supply chain, which of course also describes the sourcing of solar panels.

\citet{bakshi_signaling_2015} develop a game theoretic model of a market where reliability is uncertain, and the seller holds private information. The authors show how service contracts can be used as credible signals of product quality. \citet{gumus_supply_side_2012} analyses a similar dynamic, where a buyer must choose between a reliable but more expensive supplier and a less reliable but cheaper supplier who also holds private information about quality. Here a guarantee is used as a signal of quality. Interestingly, in relation to this article, a spot market is allowed to exist for the underlying good, thus implying that the underlying good is a commodity. Reliability here is then, presumably, associated not with the good but the supplier. Other research in the operations research of procurement with spot- or other financial markets often assume the existence of such markets \citep{zhao_demand_2015, li_buy_2018}. But to my knowledge there lacks research analysing the underlying conditions necessary for the formation of such financial markets in the operations research literature. In the context of this article, one of those conditions would be that the traded good is a commodity with a certain uniform quality level.

Early theoretical work in economics of particular relevance to this paper includes \citet{chan_prices_1982}, whom model the situation where information on quality is costly rather than directly unavailable and where quality is endogenous to the seller--in other words the seller can choose the level of quality of its product. Under these assumptions, the authors predict several equilibrium--essentially markets for both high- and low-quality products depending on the extent to which the buyer is informed.
